Bayesian exponential random graph modelling of KWL Burial network

### 2020-04-03 analysis/paper/paper.Rmd
work on method section

# Methods

@@

@@

## Statistics
We want to know

ERGM- consider transitivity by taking into account high-order k-triangles. Triangles and higher order cycles

@@

```{r model-ergm-1}
model.ergm <- burial_network_pre ~ 
  edges + # ties, a measure of density, equal to kstar(1) for undirected networks
  density +
  gwdegree(0.5, fixed = TRUE) +
  triangle # triad relation, a measure of clustering or cohesion, also called transitive triple in undirected network, can be replaced by "gwdegree"
summary(model.ergm)
```

```{r model-ergm-2}
# check out the terms: http://mailman13.u.washington.edu/pipermail/statnet_help/2010/000575.html
# also check here Morris et al. (2008)
model.2 <- burial_network_pre ~ edges + # density
  gwesp(0.2, fixed = TRUE) +  # transitivity(cohesion; triangle)
  # number means weight parameter alpha, which controls the rate of declining marginal returns
  # fixed = TRUE means the scale parameter lambda is fit as a curved exponential-family model
  # not much difference in a range of 0-1.5, the lower the value of the scaling parameter, the less likely the model is to be degenerate
  # ergm can estimate the parameter from the data by using fixed=FALSE

@@

```{r model-ergm-3}
model.3 <- burial_network_pre ~ edges +  # the overall density of the network
  nodematch('quantity') + # quantity-based homophily, categorical nodal attribute
  # the similarity of connected nodes
  gwesp(0.2, fixed = TRUE) +  # transitivity
  gwdegree(0.8, fixed = TRUE) # popularity
summary(model.3)
```

@@

```{r model-bergm}
# Specify a prior distribution: normal distribution (low density and high transitivity)
prior.mean <- c(-3, 0, 1, 0) # prior mean corresponds to mean for each parameter
# follow Alberto Caimo et al. (2015) hospital example
prior.sigma <- diag(3, 4, 4) # covariance matrix structure
# where the dimension d corresponds to the number of parameters, 𝜇 is mean vector and Σprior is a d × d covariance matrix.

>>>>

We assume burial network represents the relations among people and social structure based on the argument that 
# Methods

Our purpose is to understand the characteristics of burial network and the mechanism of the relationship influence on the pattern of accumulation of wealth during different foreign contact periods. Previous studies have shown that there are some evidence of social inequality observed on this site but the degree and causes remains unclear. To answer our question about the shifts in social inequality during and after the arrival of foreign presence, we hypothesize:

• Hypothesis 1: There are significant reciprocal structure effects in burial network before the contact
• Hypothesis 2: There are significant transitivity structure effects in burial network after the contact
• Hypothesis 3: There are significant popularity structure effects in in burial network after the contact

@@

We want to know

@@

## Statistics
ERGM- consider transitivity by taking into account high-order k-triangles. Triangles and higher order cycles

@@

```{r pre-model-ergm-1}
model.ergm <- burial_network_pre ~ 
  edges + # ties, a measure of density, equal to kstar(1) for undirected networks
  density +
  gwdegree(0.5, fixed = TRUE) +
  triangle # triad relation, a measure of clustering or cohesion, also called transitive triple in undirected network, can be replaced by "gwdegree"
summary(model.ergm)
```

```{r pre-model-ergm-2}
# check out the terms: http://mailman13.u.washington.edu/pipermail/statnet_help/2010/000575.html
# also check here Morris et al. (2008)
model.2 <- burial_network_pre ~ edges + # density
  gwesp(0.2, fixed = TRUE) +  # transitivity(cohesion; triangle)
  # number means weight parameter alpha, which controls the rate of declining marginal returns
  # fixed = TRUE means the scale parameter lambda is fit as a curved exponential-family model
  # not much difference in a range of 0-1.5, the lower the value of the scaling parameter, the less likely the model is to be degenerate
  # ergm can estimate the parameter from the data by using fixed=FALSE

@@

```{r pre-model-ergm-3}
model.3 <- burial_network_pre ~ edges +  # the overall density of the network
  nodematch('quantity') + # quantity-based homophily, categorical nodal attribute
  # the similarity of connected nodes
  gwesp(0.2, fixed = TRUE) +  # transitivity
  gwdegree(0.8, fixed = TRUE) # popularity
summary(model.3)
```

@@

```{r pre-model-bergm}
# Specify a prior distribution: normal distribution (low density and high transitivity)
prior.mean <- c(-3, 0, 1, 0) # prior mean corresponds to mean for each parameter
# follow Alberto Caimo et al. (2015) hospital example
prior.sigma <- diag(3, 4, 4) # covariance matrix structure
# where the dimension d corresponds to the number of parameters, 𝜇 is mean vector and Σprior is a d × d covariance matrix.
